Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Improve graph showing below expected grade by current grade
Rather than a barplot, doing a line and dot plot with a smooth function and error bars.

```{r retention-by-grade}
acs %>%
  group_by(current_grade) %>%
  summarize(below_grade=mean(below_exp_grade)) %>%
  ggplot(aes(x=current_grade, y=below_grade))+
  geom_col()+
  scale_y_continuous(labels=scales::percent)+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```

@@

```{r retention-by-year-grade}
acs %>%
  group_by(current_grade, year) %>%
  summarize(below_grade=mean(below_exp_grade)) %>%
  ggplot(aes(x=year, y=below_grade, group=current_grade, color=current_grade))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks=c(2010,2014,2018))+
  scale_y_continuous(labels=scales::percent)+
  scale_color_viridis_d()+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```

>>>>

```{r retention-by-grade}
acs %>%
  group_by(current_grade) %>%
  summarize(below_grade=mean(below_exp_grade),
            n=n(),
            se=sqrt((below_grade*(1-below_grade))/n)) %>%
  ggplot(aes(x=current_grade, y=below_grade, group=1,
             ymin=below_grade-1.96*se, ymax=below_grade+1.96*se))+
  geom_smooth(se=FALSE)+
  geom_line(linetype=2, color="grey30")+
  geom_point()+
  geom_linerange()+
  scale_y_continuous(labels=scales::percent)+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```

@@

```{r retention-by-year-grade}
acs %>%
  group_by(current_grade, year) %>%
  summarize(below_grade=mean(below_exp_grade)) %>%
  ggplot(aes(x=year, y=below_grade, group=current_grade, color=current_grade))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks=c(2010,2014,2018))+
  scale_y_continuous(labels=scales::percent)+
  scale_color_manual(values=rainbow(14))+
  labs(x="current grade", y="percent clearly behind grade level for age")+
  theme_bw()
```
